Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-14 preliminaries.tex
Clean up comp. indistinguishability dfn

@@

\subsection{Computational Indistinguishability}

\Ethan{Use Mahadev's definitions, but add eps param

change to subnormalized states

Need to define what it means to apply algorithm to subnormalized states

Two families of (potentially sub-normalized) states... leave author note for applying algorithms to subnormalized states; might be ok

change ``attacker" to ``distinguisher"

sec. param change from n to lambda}

\Ethan{Comment out entire section including triangle ineq.; just leave what's said above}

\begin{definition}[quantum computationally indistinguishable]\label{def:comp-indis}
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input. We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q \leq \eps.$$
And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q > \eps.$$
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

\begin{rmk}
We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
\end{rmk}

\begin{rmk}\label{rmk:trace-to-comp}
If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
\end{rmk}

\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
    \begin{align}
        \norm{D_1 -D_2}_q &\leq \eps \\ 
        \norm{D_2 -D_3}_q &\leq \eps'. 
    \end{align}
    We have 
    \begin{align}
        \norm{D_1 -D_3}_q &\leq \eps+\eps'
    \end{align}
\end{lem}
\begin{proof}
For all quantum circuits $A$ with size $\poly(n)$, we have 
\begin{align}
    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
\end{align}
so 
\begin{align}
    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \eps +\eps' \nn
\end{align}

\end{proof}

>>>>

\begin{definition}
	Let $\rho_1,\rho_2\in\cB^n$.
	We write $\rho_1\approx_{c,\varepsilon}\rho_2$ if $\rho_1$ and $\rho_2$ are \emph{$\varepsilon$-computationally indistinguishable}.
	That is, for all quantum polynomial-time distinguishers $\mathsf{D}$,
	$$\abs{\Pr\left[\mathsf(D)(\rho_1)=1\right]-\Pr\left[\mathsf(D)(\rho_2)=1\right]}\leq\varepsilon.$$
\end{definition}

We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized outputs on subnormalized inputs.
We also extend it to distributions, which can be treated as mixed states.

\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
    \begin{align}
		D_1\approx_{c, \varepsilon}D_2\\
		D_2\approx_{c, \varepsilon'}D_3.
    \end{align}
    We have 
    \begin{align}
		D_1\approx_{c, \varepsilon+\varepsilon'}D_3.
    \end{align}
\end{lem}

@@
